\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{mathptmx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
            {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
\textbf{\huge \scshape João Victor Santos da Costa} \\
\small
+55 55 99217-7324 |
 \href{mailto:victorsantos.ft18@gmail.com}{
 victorsantos.ft18@gmail.com} |
 \href{https://linkedin.com/in/viquitor}{linkedin.com/in/viquitor} \\
 {For more details, visit my site: \href{https://viquitor-me.vercel.app}{My
Social Links}}
\end{center}

%-----------Experience-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
{cafezinho}{Dec 2023 -- Present}
{Trainee}{Remote}
\resumeItemListStart
\resumeItem{\textbf{Front-end Developer} Conceptualizes, designs, and refines system functionalities, ensuring an optimal user experience and robust system performance. Successfully improved user interface speed by 20\% through code optimization.}
\resumeItem{\textbf{Scrum Master} Orchestrates agile ceremonies, including sprint planning and retrospective sessions, to foster team cohesion and adherence to agile methodologies. Reduced sprint planning time by 50\% through efficient enhancement of agile practices. Oversees backlog prioritization, product vision, and feature validation.}
\resumeItem{\textbf{Tech Lead} Provides strategic technical direction, approves Pull Requests (PRs), and ensures adherence to code quality and design system standards. Led a team of 16 developers, increasing project completion rate by 40\%.}
\resumeItem{\textbf{Software Engineer} Directs the development team, allocates tasks strategically, and ensures timely project delivery. Evaluates and approves software artifacts for quality assurance, resulting in a 20\% reduction in post-release defects.}
\resumeItemListEnd

\resumeSubheading
{ERP Vendas}{July 2022 -- October 2022}
{Trainee}{Remote}
\resumeItemListStart
\resumeItem{\textbf{Full Stack Developer} Diagnosed and resolved complex bugs, while spearheading the development of innovative tools, reducing system downtime by 10\%.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Extracurriculars-----------
\section{PROJECTS}
\resumeSubHeadingListStart

\resumeSubheading
{CRUD API}{July 2024}
{Java, Spring, MySQL}{}
\resumeItemListStart
\resumeItem{Engineered a REST API from inception using Java with Spring Boot, utilizing MySQL for data persistence and Flyway for seamless migrations.}
\resumeItem{Harmonized API controller responses with standardized HTTP status codes, incorporating custom exceptions and enums for enhanced response management, reducing error response time by 20\%.}
\resumeItem{Integrated Spring Security for robust authentication and access control, employing JSON Web Token (JWT) for secure session management, increasing security compliance by 30\%.}
\resumeItem{Applied SOLID principles and Clean Code practices, ensuring high code quality and maintainability, which reduced technical debt by 25\%.}
\resumeItemListEnd
{For more details, visit my GitHub repository: \href{https://github.com/Jao-Viquitor/GEM}{GEM API}.\\}


\resumeSubheading
{Portifolio}{July 2024}
{React, Vite, CSS}{}
\resumeItemListStart
\resumeItem{Crafted a dynamic portfolio website to effectively showcase my projects and technical proficiencies. Enhanced site loading speed by 35\% through performance optimizations.}
\resumeItem{Implemented responsive design using CSS to enhance user engagement across devices, leading to a 50\% increase in mobile traffic.}
\resumeItemListEnd
{For more details, visit my site: \href{https://viquitor.vercel.app}{Portifolio}.\\}

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading
{Unopar}{Remote}
{Currently studying the 5th semester of Software Engineering}{Set. 2023 -- present}
\resumeSubheading
{Universidade Federal do Pampa}{Alegrete, RS}
{Completed 6/8 semesters towards a Bachelor of Engineer Software}{Mar. 2017 -- Sept 2022}
\resumeSubHeadingListEnd

%-----------Skills and Interests-----------
\section{SKILLS \& INTERESTS}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\vspace{1mm}
\textbf{Languages}{: \textbf{Native}: Portuguese -- \textbf{Intermediate}: English \& Spanish} \\
\vspace{1mm}
\textbf{Technologies:} {Java, Kotlin, Dart, Javascript, PHP, Prolog, Haskell, Typescript, SQL, C \& C\#, CSS, HTML, Excel} \\
\vspace{1mm}
\textbf{Frameworks}{: Flutter, React, Spring, Laravel, Jetpack Compose, TailwindCSS, Bootstrap, MySQL, PostgreSQL, MongoDB} \\
\vspace{1mm}
\textbf{Developer Tools}{: IntelliJ, GitHub, Figma, Vercel, WordPress, Jira \& Trello} \\
\vspace{1mm}
\textbf{Soft Skills}{: Communication, Teamwork, Problem-Solving, Leadership, Time Management, Adaptability, Critical Thinking, Empathy, Collaboration, Creativity, Negotiation, Decision-Making} \\
\vspace{1mm}
}}
\end{itemize}


\end{document}
